Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2023-01-31 reports/supplement/supplement_0.9.1.Rmd
update supplement

For comparability with the [Bush et al publication 2017](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. In our work, we only make comparisions where the outcome is the same when a log- or and arithmetic-scale of oxygen diffusivity was used. For example, compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). The direction of the effects does not depend on the log/arithmetic scale decision.

In contrast, we avoid comparisons where the outcome would differ when a log- or and arithmetic-scale of oxygen diffusivity was used. An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-anoxic transition. We avoid this comparison of magnitudes because with a log scale the diversity effect is larger for the oxic-anoxic transition (Figure \@ref(fig:fig-log-nonlog)n), while on an arithmetic scale the diversity effect is larger for the anoxic-oxic transition (Figure \@ref(fig:fig-log-nonlog)o).

>>>>

For comparability with the [Bush et al publication (2017)](https://www.nature.com/articles/s41467-017-00912-x), we use a log-scale of the oxygen diffusivity gradient when displaying the effect of trait variation on tipping point positions. In our work, we only make comparisons where the outcome is the same when a log- or an arithmetic-scale of oxygen diffusivity was used. For example, we compare the direction of the diversity effects of the three functional groups on the resilience of the ecosystem state that they dominate (CB: oxic state, i.e. oxic-anoxic tipping point; SB and PB: anoxic state, i.e. anoxic-oxic tipping point). The direction of the effects does not depend on the log/arithmetic scale decision.

In contrast, we avoid comparisons where the outcome would differ when a log- or an arithmetic-scale of oxygen diffusivity was used. An example of a comparison that we avoid is of the magnitude of the diversity effect between the oxic-anoxic transition and the anoxic-oxic transition. We avoid this comparison of magnitudes because with a log scale the diversity effect is larger for the oxic-anoxic transition (Figure \@ref(fig:fig-log-nonlog)n), while on an arithmetic scale the diversity effect is larger for the anoxic-oxic transition (Figure \@ref(fig:fig-log-nonlog)o).
